Asymmetric continuous prediction bands for assessing the validity of smooth biomechanical curve data

### 2021-08-23 paper.Rmd
Modify shock data

#### Smooth wave data with nonlinear trend (constant variance)

@@

#### Data with non-gaussian (Weibull distributed) error (no trend)

@@

>>>>

#### Curves with nonlinear trend (constant variance)

@@

#### Curves with non-gaussian (Weibull distributed) error (no trend)

@@

#### Curves with (missing) peaks

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "shock", dir.data)
